Interoception Scale - Data Cleaning

### 2024-11-29 study1/analysis/1_cleaning.qmd
finished TODO on cleaning script

---
title: "Interoception Scale - Data Cleaning"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

@@

**TODO: Add feedback comments table**

@@

We removed `r length(outliers$attentionchecks)` (`insight::format_percent(length(outliers$attentionchecks) / nrow(df))`) participants for having failed at least 1 attention check (out of 8).

@@

**TODO: Add a little paragraph explaining what it is etc.**
We removed `r length(outliers$distance)` (`insight::format_percent(length(outliers$distance) / nrow(df))`) participants based on multivariate distance.

@@

::: panel-tabset

## Summary

>>>>

---
title: "Interoception Scale - Data Cleaning"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
bibliography: references.bib
---

@@

### Comments

```{r}
data.frame(Condition = df$Condition,
          Comments = df$Experiment_Feedback) |> 
  filter(!tolower(Comments) %in% c(NA, "None", "no", "none", "No thank you", "no thank you", "no not at all", "no thanks", "No comment", "No", "nil", "N.A", "n/a", "N/A", "na", "Not Really")) |> 
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) 
```

@@

We removed `r length(outliers$attentionchecks)` (`r insight::format_percent(length(outliers$attentionchecks) / nrow(df))`) participants for having failed at least 1 attention check (out of 8).

@@

Mahalanobis distance [@demaesschalck2000] is commonly used to detect multivariate outliers, which are data points with unusual combinations of scores on two or more variables [@filzmoser2016]. This distance is calculated relative to the centroid—a central point where the means of all variables intersect—with larger distances indicating greater deviation from the center.

This measure takes into account correlations within the dataset, which is especially useful when trying to refine and validate a questionnaire with overlapping itmes.

We removed `r length(outliers$distance)` (`r insight::format_percent(length(outliers$distance) / nrow(df))`) participants based on multivariate distance.

@@

::: panel-tabset
## Summary
